---
title: 
output: html_document
css: "my1.css"
---

<style>
.main-container {
  max-width: 100% !important;
}
</style>

 <div class="part1">
<h1>SpaceX: Gene Co-Expression Network Estimation for
 Spatial Transcriptomics: Installation</h1>
 
<div class="tab">
<button class="tablinks button" onclick="location.href='htmlrmark1.html'">Home</button>
<button class="tablinks button" onClick="location.href='my2.html'">Installation</button> 
<button class="tablinks button" onclick="location.href='my3.html'">Examples</button>
<button class="tablinks button" onclick="location.href='my4.html'">Visualization</button>
<button class="tablinks button" onclick="location.href='my5.html'">Supplemental File</button>
<button class="tablinks button" onclick="location.href='my6.html'">Contact</button>
<button class="tablinks button" onclick="location.href='my7.html'">Citation</button>
<button class="tablinks button" onclick="location.href='my8.html'">View on Github</button>
<button class="tablinks button" onclick="location.href='my9.html'">Acknowledgement</button>
 </div>
  </div>

 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position=c("top","right"))
```

This package requires a Fortran compiler in order to work. Here are the instructions:

* Windows: install the Rtools package that is appropriate for your version of R
* Mac: Go to this website and follow the instructions: (https://mac.R-project.org/tools/)
* Linux: From a terminal, do the following: 
`sudo apt install gcc.
`
That will bring in multiple compilers.

The package requires a dependency that is not available on CRAN. Install it with:
```{r, eval=FALSE}
remotes::install_github("rdevito/MSFA")
```


You can install the released version of SpaceX from (https://github.com/SatwikAch/SpaceX) with:

```{r,eval=FALSE}
devtools::install_github("SatwikAch/SpaceX")
library(SpaceX)
```

 

