<<<<<<< HEAD
---
title: "Installation"
output: html_document
---

 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position=c("top","right"))
```

This package requires a Fortran compiler in order to work. Here are the instructions:

* Windows: install the Rtools package that is appropriate for your version of R
* Mac: Go to this website and follow the instructions: (https://mac.R-project.org/tools/)
* Linux: From a terminal, do the following: 
`sudo apt install gcc.
`
That will bring in multiple compilers.

The package requires a dependency that is not available on CRAN. Install it with:
```{r, eval=FALSE}
remotes::install_github("rdevito/MSFA")
```


You can install the released version of SpaceX from (https://github.com/SatwikAch/SpaceX) with:

```{r,eval=FALSE}
devtools::install_github("SatwikAch/SpaceX")
library(SpaceX)
```

  <a href="htmlrmark1.html">Return to original page</a>


=======
---
title: "another test for html"
output: html_document
---

My House

  <p>How to move back and forth</p>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

  ```{r}
  print(2*pi)
  ```
  
  
  <a href="htmlrmark1.html">Return to original page</a>
</body>
</html>

>>>>>>> 9d961eb4dcfb477c430f9261230b63c9963c863e
