---
title:
output: html_document
css: "my1.css"
bibliography: reference.bib
---

<style>
.main-container {
  max-width: 100% !important;
}
</style>


 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position=c("top","right"))
```

 <div class="part1">
<h1>SpaceX: Gene Co-Expression Network Estimation for
 Spatial Transcriptomics: Citation</h1>
 
<div class="tab">
<button class="tablinks button" onclick="location.href='htmlrmark1.html'">Home</button>
<button class="tablinks button" onClick="location.href='my2.html'">Installation</button> 
<button class="tablinks button" onclick="location.href='my3.html'">Examples</button>
<button class="tablinks button" onclick="location.href='my4.html'">Visualization</button>
<button class="tablinks button" onclick="location.href='my5.html'">Supplemental File</button>
<button class="tablinks button" onclick="location.href='my6.html'">Contact</button>
<button class="tablinks button" onclick="location.href='my7.html'">Citation</button>
<button class="tablinks button" onclick="location.href='my8.html'">View on Github</button>
<button class="tablinks button" onclick="location.href='my9.html'">Acknowledgement</button>
 </div>
  </div>


<p>

<h2><div class="language-plaintext highlighter-rouge"><div class="highlight"><pre class="highlight"><code>@article{acharyya2021spacex,
    author = {Acharyya, Satwik and Zhou, Xiang and Baladandayuthapani, Veerabhadran},
    title = {SpaceX: Gene Co-expression Network Estimation for Spatial Transcriptomics},
    journal = {bioRxiv},
    year = {2021}
} 
</code></pre></div></div>
</h2>





 


